ESRC SDAI Application - Understanding domestic abuse using Big Data

### 2019-07-23 JeS_fields.tex
wmp summary and minor edits

We have 3 core objectives.

1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales. Through the rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, we will provide a deeper understanding of the environments perpetuating domestic abuse in England and Wales. While we will only use UK-specific data, insights from these analyses will likely to be applicable to non-UK contexts.

>>>>

We have 4 core objectives.

1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales. Through the rigorous validation of insights from existing, mostly quantitative investigations using a UK-wide dataset, we will provide a deeper understanding of the environments perpetuating domestic abuse in England and Wales. While we will only use UK-specific data, insights from these analyses will likely to be applicable to non-UK contexts.
